---
title: "EMPIA Analyses 2.0"
author: "Ashlie"
date: "2024-08-11"
output: html_document
---

```{r setup}

# Libraries
pacman::p_load(knitr, # rendering of .Rmd file
               lme4, # model specification/estimation
               afex, # anova and deriving p-values via LRTs from lmer
               broom.mixed, # extracting data from model fits
               faux, # generate correlated values
               tidyverse, # data wrangling and visualization 
               ggridges, # visualization
               viridis, # color schemes for visualization
               kableExtra, # helps with knitting the .Rmd file
               cowplot, # visualization tool to include multiple plots
               ggrain, # visualization tool for raincloud plots
               dplyr, # data manipulation tools
               here, # controlling directories/reproducibility
               tidyr, # formatting package
               readr, # data importation
               Hmisc, # visualization
               emmeans, # estimation of marginal means and contrasts
               sjstats, # estimation of marginal means and contrasts
               lmerTest, # deriving p-values from lmer
               MuMIn, # ?
               sjPlot, # APA formatting of numerical output
               car, # data wrangling and visualization,
               magrittr, # to use %>%
               ggpubr, # ? (Rose had it in her script)
               broom, # ? (Rose had it in her script)
               Matrix, # model specification/estimation,
               multcomp, # multiple comparison adjustments
               forcats, # organizing visualizations
               gtools, # data manipulation/wrangling
               fuzzySim, # FDR correction,
               ez, # anova
               apaTables, # visualization of anova output
               #renv # package versioning/reproducibility
               )

# Global theme set
set.seed(1234) # set random seed for reproducibility

knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)

#theme_set(theme_bw(base_size = 13) + theme(text = element_text(size=13), 
                             #axis.title=element_text(size=12),
                             #strip.text = element_text(margin=margin(2,0,2,0)), 
                             #panel.grid = element_blank()))

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE, fig.width=10, fig.height=8, fig.fullwidth=TRUE)

plot_theme <- 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18), 
        axis.text.x = element_text(size = 13), 
        axis.title.x = element_text(size = 13), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 13),
        strip.background = element_rect(color="white", fill="white", linewidth = 1.5, linetype="solid"))

options(scipen=999)
```

# Demographic Data
## Data Manipulations
```{r}
# Load data (1 data frame)
demo_data <- read.csv(here("SYP Data", "Participant Info.csv"),stringsAsFactors=TRUE) # N400 mean amplitude data

# Format data
demo_data %<>%
  mutate(group = factor(Group),
         fluency = factor(Fluency),
         sex.c = as.numeric(Sex) - 1.5,
         age = as.numeric(Age),
         age.c = as.numeric(scale(Age, center = TRUE, scale = FALSE)),
         years.since.stroke.c = as.numeric(scale(Years.since.stroke, center = TRUE, scale = FALSE)),
         WAB.AQ = as.numeric(WAB.AQ),
         wab.c = as.numeric(scale(WAB.AQ, center = TRUE, scale = FALSE)),
         BNT = as.numeric(BNT),
         bnt.c = as.numeric(scale(BNT, center = TRUE, scale = FALSE)),
         RCPM = as.numeric(RCPM),
         rcpm.c = as.numeric(scale(RCPM, center = TRUE, scale = FALSE)),
         RCBA = as.numeric(RCBA),
         rcba.c = as.numeric(scale(RCBA, center = TRUE, scale = FALSE)),
         Trails.A.min = as.numeric(Trails.A.min),
         trailsa.c = as.numeric(scale(Trails.A.min, center = TRUE, scale = FALSE)),
         Trails.B.min = as.numeric(Trails.B.min),
         trailsb.c = as.numeric(scale(Trails.B.min, center = TRUE, scale = FALSE)))
str(demo_data)

# Create some data subsets
includedsubs_data <- subset(demo_data, Exclude. == "0")
includedpwa_data <- subset(includedsubs_data, Group == "aphasic")
includedoc_data <- subset(includedsubs_data, Group == "old control")

# Notes:
# Group default reference level = aphasic
# Aphasia Type = fluency; default reference level = fluent
# For sex, female = -0.5 (after centering), male = 0.5 (after centering)
```

## Descriptives
```{r}
includedsubs_data %>%
  group_by(Group)%>%
  summarise_at('age', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()
```
## Analyses
```{r}
age_model <- t.test(age ~ Group,includedsubs_data)
age_model
```




# Behavioral Data
## Probe Detection Data
### Data Manipulations
```{r}
# Load data
Response_Accuracy <- read.csv(here("SYP Data", "Submission 2 Data", "Behavioral Data", "Response Accuracy Data (updated).csv"), stringsAsFactors=TRUE) # probe detection data

# Format data
Response_Accuracy %<>%
  mutate(Group = factor(Group), 
         trial.type = factor(Trial.Type, levels = c("animal prime", "unprimed animal target", "primed animal target")),
         per_resp = as.numeric(per_resp),        
         per_resp_arc = as.numeric(per_resp_arc))
str(Response_Accuracy)

# Create some data subsets
Response_Accuracy <- subset(Response_Accuracy, exclude. == "0")
```
### Descriptives
```{r}
Response_Accuracy %>%
  group_by(Group,trial.type)%>%
  summarise_at('per_resp', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group,trial.type, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()

Response_Accuracy %>%
  group_by(Group)%>%
  summarise_at('per_resp', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()

```
### Analyses
```{r}
Response_Accuracy$Group <- relevel(Response_Accuracy$Group, ref = "Old Control")
#Response_Accuracy$Group <- relevel(Response_Accuracy$Group, ref = "Aphasic")

Response_Accuracy$Trial.Type <- factor(Response_Accuracy$Trial.Type, levels = c("animal prime", "unprimed animal target", "primed animal target"))
contrasts(Response_Accuracy$Trial.Type)<-contr.treatment(levels(Response_Accuracy$trial.type))/3
contrasts(Response_Accuracy$Group)<-contr.treatment(levels(Response_Accuracy$Group))/2
resp_acc <- lmer(per_resp_arc ~ 1+ Group*Trial.Type + (1|Participant.ID), data=Response_Accuracy)
tab_model(resp_acc, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df = TRUE)

Response_Accuracy$Trial.Type <- factor(Response_Accuracy$Trial.Type, levels = c("unprimed animal target", "primed animal target","animal prime"))
contrasts(Response_Accuracy$Trial.Type)<-contr.helmert(levels(Response_Accuracy$Trial.Type))/3
contrasts(Response_Accuracy$Group)<-contr.treatment(levels(Response_Accuracy$Group))/2
resp_acc <- lmer(per_resp_arc ~ 1+ Group*Trial.Type + (1|Participant.ID), data=Response_Accuracy)
tab_model(resp_acc, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df = TRUE)


# emmeans(resp_acc, pairwise~Group | trial.type, adjust = "none")
# emmeans(resp_acc, pairwise~trial.type | Group, adjust = "none")
```

## Reaction Time/Behavarial Priming Effects Data
### Data Manipulations
```{r}
# Load data
RTs <- read.csv(here("SYP Data", "Submission 2 Data", "Behavioral Data", "RT Data (updated).csv"), stringsAsFactors=TRUE) # behavioral priming (RT) data

# Format data
RTs %<>%
  mutate(Group = factor(Group), 
         target.status = factor(Target.Status),
         TargetWordRT = as.numeric(TargetWordRT),        
         resp.type = factor(Response.Type),
         target.word = factor(TargetWord))
str(RTs)

RTs <- subset(RTs, Exclude. == "0" & Target.Response.Outlier. == "0" & resp.type == "hit")
str(RTs)
```

### Descriptives
```{r}
RTs %>%
  group_by(Group,target.status)%>%
  summarise_at('PrimeWord.RT', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group,target.status, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()

RTs %>%
  group_by(Group)%>%
  summarise_at('PrimeWord.RT', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()
```

### Analyses
```{r}
RTs$Group <- relevel(RTs$Group, ref = "Old Control")
#RTs$Group <- relevel(RTs$Group, ref = "Aphasic")
RTs$target.status <- relevel(RTs$target.status, ref = "unprimed")
#RTs$target.status <- relevel(RTs$target.status, ref = "primed")


RTs_model <- lmer(PrimeWord.RT ~ 1+ Group*target.status + (1|Participant.ID) + (1|target.word), data=RTs)
tab_model(RTs_model, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df=TRUE)
```

## Recognition Task Data
### Data Manipulations
```{r}
# Load data
Recog_Data <- read.csv(here("SYP Data", "Submission 1 Data", "Recog Data", "Included Recog Data.csv"), stringsAsFactors=TRUE) # behavioral priming (RT) data

# Format data
Recog_Data %<>%
  mutate(Group = factor(Group), 
         TypeRecog = factor(TypeRecog),
         PerRecog = as.numeric(PerRecog),
         pr_arc = as.numeric(pr_arc))
str(Recog_Data)
```

### Descriptives/Visualizations
```{r}
Recog_Data %>%
  group_by(Group)%>%
  summarise_at('pr_arc', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()

Recog_Data %>%
  group_by(Group,TypeRecog)%>%
  summarise_at('pr_arc', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group,TypeRecog, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()

Recog_Data %>%
  #mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(TypeRecog, PerRecog, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Percent Recognized") +
  xlab("Stimulus Type")
```

### Analyses
```{r}
Recog_Data$Group <- relevel(Recog_Data$Group, ref = "Old Control")
#Recog_Data$Group <- relevel(Recog_Data$Group, ref = "Aphasic")
 
Recog_Data$TypeRecog <- factor(Recog_Data$TypeRecog, levels = c("Foil", "Unmasked", "Masked"))
contrasts(Recog_Data$TypeRecog)<-contr.treatment(levels(Recog_Data$TypeRecog))/3
contrasts(Recog_Data$Group)<-contr.treatment(levels(Recog_Data$Group))/2
recog_acc <- lmer(pr_arc ~ 1+ Group*TypeRecog + (1|Participant.ID), data=Recog_Data)
tab_model(recog_acc, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df = TRUE)

Recog_Data$TypeRecog <- factor(Recog_Data$TypeRecog, levels = c("Masked", "Unmasked", "Foil"))
contrasts(Recog_Data$TypeRecog)<-contr.helmert(levels(Recog_Data$TypeRecog))/3
contrasts(Recog_Data$Group)<-contr.treatment(levels(Recog_Data$Group))/2
recog_acc <- lmer(pr_arc ~ 1+ Group*TypeRecog + (1|Participant.ID), data=Recog_Data)
tab_model(recog_acc, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df = TRUE)
contrasts(Recog_Data$TypeRecog)
```


# ERP Data
## Artifact Rejection Data
### Data Manipulations
```{r}
# Load data (2 data frames)
AR_Pers <- read.csv(here("SYP Data","Submission 1 Data", "Artifact Rejection Data", "Artifact Rejection Percentages.csv"),stringsAsFactors=TRUE) # artifact rejection percentage data
AR_Pers_nototal <- read.csv(here("SYP Data","Submission 1 Data", "Artifact Rejection Data", "Artifact Rejection Percentages.csv"),stringsAsFactors=TRUE) # artifact rejection percentage data without "total" bin

# Format data
AR_Pers %<>%
  mutate(Group = factor(Group), 
         Bin = factor(Bin),
         TotalPR_arc = as.numeric(TotalPR_arc))
str(AR_Pers)

AR_Pers_nototal %<>%
  mutate(Group = factor(Group), 
         Bin = factor(Bin),
         TotalPR_arc = as.numeric(TotalPR_arc))
str(AR_Pers)

# Create some data subsets
AR_Pers <- subset(AR_Pers, Exclude. == "0") #, Participant.ID != "t117" & Participant.ID != "t125")
AR_Pers_nototal <- subset(AR_Pers, Exclude. == "0")
```

### Descriptives
```{r}
AR_Pers %>%
  group_by(Group)%>%
  summarise_at('TotalPR_arc', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(Group, n, mean, sd, median, min, max)%>%
  mutate(total.n = sum(n))%>%
  knitr::kable()
```
### Analyses
```{r}
contrasts(AR_Pers_nototal$Bin)<-contr.sum(levels(AR_Pers_nototal$Bin))/9
contrasts(AR_Pers_nototal$Group)<-contr.sum(levels(AR_Pers_nototal$Group))/2

AR_Pers_model <- lmer(TotalPR_arc ~ 1+ Group*Bin + (1|Participant.ID), data=AR_Pers_nototal)
tab_model(AR_Pers_model, show.se = TRUE,show.ci = FALSE, show.stat = TRUE)


emmeans(AR_Pers_model, pairwise~Group, adjust = "none")
emmeans(AR_Pers_model, pairwise~Bin, adjust = "none")
emmeans(AR_Pers_model, pairwise~Group | Bin, adjust = "none")

```

## N400 Data
### Data Manipulations
```{r}
# Load data (2 data frames)
n400_data <- read.csv(here("SYP Data","Submission 2 Data", "Mean Amplitudes", "N400 Mean Amps.csv"),stringsAsFactors=TRUE) # N400 mean amplitude data
n400_diffwave_data <- read.csv(here("SYP Data","Submission 2 Data", "Mean Amplitudes", "N400 Diff Waves Data.csv"),stringsAsFactors=TRUE) # N400 difference wave mean amplitude data

# Format data
n400_data %<>%
  mutate(Group = factor(Group), 
         Aphasia.Type = factor(Aphasia.Type),
         Condition = factor(Condition, levels=c("Non-animal_targets/no_primes","Delayed_masked_primes","Delayed_visible_primes","Immediate_masked_primes","Unrelated_primes")),
         Prime.Latency = factor(Prime.Latency),
         Prime.Visibility = factor(Prime.Visibility),
         Electrode = factor(Electrode),
         Region = factor(Region),
         Hemisphere = factor(Hemisphere),
         Mean.Amplitude = as.numeric(Mean.Amplitude),
         Component = factor(Component),
         sex.c = as.numeric(Sex) - 1.5,
         age.c = as.numeric(scale(Age, center = TRUE, scale = FALSE)),
         years.since.stroke.c = as.numeric(scale(Years.since.stroke, center = TRUE, scale = FALSE)),
         WAB.AQ = as.numeric(WAB.AQ),
         wab.c = as.numeric(scale(WAB.AQ, center = TRUE, scale = FALSE)),
         BNT = as.numeric(BNT),
         bnt.c = as.numeric(scale(BNT, center = TRUE, scale = FALSE)),
         RCPM = as.numeric(RCPM),
         rcpm.c = as.numeric(scale(RCPM, center = TRUE, scale = FALSE)),
         RCBA = as.numeric(RCBA),
         rcba.c = as.numeric(scale(RCBA, center = TRUE, scale = FALSE)),
         Trails.A.min = as.numeric(Trails.A.min),
         trailsa.c = as.numeric(scale(Trails.A.min, center = TRUE, scale = FALSE)),
         Trails.B.min = as.numeric(Trails.B.min),
         trailsb.c = as.numeric(scale(Trails.B.min, center = TRUE, scale = FALSE)))
str(n400_data)

n400_diffwave_data %<>%
  mutate(Group = factor(Group), 
         Condition = factor(Condition, levels=c("np_minus_dmp","np_minus_dvp","np_minus_imp","up_minus_imp")),
         Electrode = factor(Electrode),
         Mean.Amplitude = as.numeric(Mean.Amplitude))
str(n400_diffwave_data)

# Create some data subsets
n400chans_data <- subset (n400_data,!grepl('T7|T8|AF3|AF4|Fp1|Fp2|Fpz',Electrode))

# Notes:
# Aphasia Type = fluency; default reference level = fluent
# Condition (for N400 data) = target condition; reference level (set above) = non-animal targets/no primes
# Condition (for N400 difference wave data) = difference wave condition;  reference level (set above) = No Primes - Delayed Masked Primes
# Region = anteriority/posteriority; default reference level = Central
# Hemisphere = laterality; default reference level = Left
# For sex, female = -0.5 (after centering), male = 0.5 (after centering)
```

### Descriptives
```{r}
# N400 mean amplitudes by groupe, condition, region, and hemisphere
n400_data_grouped1 <- group_by(n400chans_data, Group, Condition, Region, Hemisphere)
summarise(n400_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amplitude),
  std = sd(Mean.Amplitude)
    )

# N400 mean amplitudes by group and condition (collapsed across region and hemisphere)
n400_data_grouped2 <- group_by(n400chans_data, Group, Condition)
summarise(n400_data_grouped2, # summarize operation by group
  mean = mean(Mean.Amplitude),
  std = sd(Mean.Amplitude)
    )
```

### Visualizations
```{r}
# N400 mean amplitude (collapsed across group, condition, region, and hemisphere)
hist(n400chans_data$Mean.Amplitude)
boxplot(n400_data$Mean.Amplitude)

# N400 mean amplitude by group (collapsed across condition, region, and hemisphere)
plot(Mean.Amplitude ~ Group, data = n400chans_data)

# N400 mean amplitude by condition (collapsed across group, region, and hemisphere)
plot(Mean.Amplitude ~ Condition, data = n400chans_data)

# N400 mean amplitude by region (collapsed across group, condition, and hemisphere)
plot(Mean.Amplitude ~ Region, data = n400chans_data)

# N400 mean amplitude by hemisphere (collapsed across group, condition, and region)
plot(Mean.Amplitude ~ Hemisphere, data = n400chans_data)

# N400 mean amplitude by group and condition (collapsed across region and hemisphere)
n400chans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("")

# N400 mean amplitude by group and condition and region (collapsed across hemisphere)
n400chans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Condition") +
  facet_wrap(~ factor(Region, c("Frontopolar","Frontal","Central","Parietal","Occipital")), nrow = 1)

# N400 mean amplitude by group and condition and hemisphere (collapsed across region)
n400chans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Condition") +
  facet_wrap(~ Hemisphere, nrow = 1)

# N400 mean amplitude by group, condition, region, and hemisphere
n400chans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(x=Condition, y=Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("Frontopolar","Frontal","Central","Parietal","Occipital")))

# N400 mean amplitude by group and condition
n400chans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Delayed masked primes
delayed_masked_data <- subset(n400chans_data, Condition == "Delayed_masked_primes" | Condition == "Unrelated_primes" | Condition == "Non-animal_targets/no_primes")
delayed_masked_data %>%
  mutate(Condition = fct_relevel(Condition,"Non-animal_targets/no_primes","Delayed_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Delayed visible primes
delayed_visible_data <- subset(n400chans_data,  Condition == "Delayed_visible_primes" | Condition == "Unrelated_primes" | Condition == "Non-animal_targets/no_primes")
delayed_visible_data %>%
  mutate(Condition = fct_relevel(Condition,"Non-animal_targets/no_primes","Delayed_visible_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Delayed primes
delayed_data <- subset(n400chans_data, Condition == "Delayed_masked_primes" | Condition == "Delayed_visible_primes")
delayed_data %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Immediate masked primes
immediate_data<- subset(n400chans_data, Condition == "Immediate_masked_primes" | Condition == "Unrelated_primes" | Condition == "Non-animal_targets/no_primes")
immediate_data %>%
  mutate(Condition = fct_relevel(Condition,"Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Masked primes
masked_data<- subset(n400chans_data, Condition == "Immediate_masked_primes" | Condition == "Delayed_masked_primes")
masked_data %>%
  mutate(Condition = fct_relevel(Condition,"Immediate_masked_primes","Delayed_masked_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# N400 priming difference by group and condition (collapsed across region and hemisphere) - more negative = greater priming effect
n400_diffwave_data %>%
  mutate(Condition = fct_relevel(Condition,"np_minus_dvp","np_minus_dmp","up_minus_imp","np_minus_imp")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Priming Difference") +
  xlab("Priming Condition") 

# Delayed primes comparison
delayed_diffwaves_data<- subset(n400_diffwave_data, Condition == "np_minus_dvp" | Condition == "np_minus_dmp")
delayed_diffwaves_data %>%
  mutate(Condition = fct_relevel(Condition,"np_minus_dvp","np_minus_dmp")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Priming Difference") +
  xlab("Priming Condition") 

# Masked primes comparison
masked_diffwaves_data<- subset(n400_diffwave_data, Condition == "up_minus_imp" | Condition == "np_minus_dmp"| Condition == "np_minus_imp")
masked_diffwaves_data %>%
  mutate(Condition = fct_relevel(Condition,"up_minus_imp","np_minus_dmp", "np_minus_imp")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Priming Difference") +
  xlab("Priming Condition") 

```

### Analyses
```{r}
n400chans_data$Condition <- factor(n400chans_data$Condition, levels=c("Non-animal_targets/no_primes","Delayed_visible_primes","Delayed_masked_primes","Immediate_masked_primes","Unrelated_primes"))
contrasts(n400chans_data$Condition)<-contr.treatment(levels(n400chans_data$Condition))/5

# n400chans_data$Condition <- factor(n400chans_data$Condition, levels=c("Delayed_visible_primes","Delayed_masked_primes","Immediate_masked_primes","Unrelated_primes","Non-animal_targets/no_primes"))
# contrasts(n400chans_data$Condition)<-contr.sdif(levels(n400chans_data$Condition))/5

#n400chans_data$Group <- relevel(n400chans_data$Group, ref = "Old Control")
n400chans_data$Group <- relevel(n400chans_data$Group, ref = "Aphasic")
contrasts(n400chans_data$Group)<-contr.treatment(levels(n400chans_data$Group))/2

# Run the model
n400_omnibus <- lmer(Mean.Amplitude ~ Condition*Group + (1|Participant.ID) + (1|Electrode), data=n400chans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) 
tab_model(n400_omnibus, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df=TRUE)


# n400_omnibus_emm <- emmeans(n400_omnibus, pairwise ~ Condition | Group, adjust = "none")
# n400_omnibus_emm
# tidy(pairs(n400_omnibus_emm, adjust="none"))%>%
#    mutate(signif = stars.pval(p.value))


n400_diffwave_data$Group <- relevel(n400_diffwave_data$Group, ref = "Old Control")
n400_diffwave_data$Group <- relevel(n400_diffwave_data$Group, ref = "Aphasic")
contrasts(n400_diffwave_data$Condition)<-contr.treatment(levels(n400_diffwave_data$Condition))/5
contrasts(n400_diffwave_data$Group)<-contr.treatment(levels(n400_diffwave_data$Group))/2

# Run the model
n400_diffwaves <- lmer(Mean.Amplitude ~ Condition*Group + (1|Participant.ID) + (1|Electrode), data=n400_diffwave_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) 
tab_model(n400_diffwaves, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df=TRUE)
```


## P300 Data
### Data Manipulations
```{r}
# Load data
p300_data <- read.csv(here("SYP Data","Submission 2 Data", "Mean Amplitudes", "P300 Mean Amps.csv"),stringsAsFactors=TRUE) # p300 mean amplitude data

# Format data
p300_data %<>%
  mutate(Group = factor(Group), 
         Condition = factor(Condition), #levels=c("Non-animal_targets/no_primes","Delayed_masked_primes","Delayed_visible_primes","Immediate_masked_primes","Unrelated_primes")),
         Electrode = factor(Electrode),
         Mean.Amplitude = as.numeric(Mean.Amplitude))
str(p300_data)

# Create some data subsets
p300chans_data <- subset (p300_data,!grepl('T7|T8|AF3|AF4|Fp1|Fp2|Fpz',Electrode))
p300prime_data <-subset(p300chans_data, Condition == "Animal_primes" | Condition == "Non-animal_primes")
p300target_data <-subset(p300chans_data, Condition == "Non-animal_targets/no_primes" | Condition == "Animal_targets")

# Notes:
# Condition (for p300 data) = target condition; reference level (set above) = non-animal targets/no primes
# Condition (for p300 difference wave data) = difference wave condition;  reference level (set above) = No Primes - Delayed Masked Primes
# Region = anteriority/posteriority; default reference level = Central
# Hemisphere = laterality; default reference level = Left
# For sex, female = -0.5 (after centering), male = 0.5 (after centering)
```

### Descriptives
```{r}
# p300 mean amplitudes by groupe, condition, region, and hemisphere
p300_data_grouped1 <- group_by(p300chans_data, Group, Condition, Region, Hemisphere)
summarise(p300_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amplitude),
  std = sd(Mean.Amplitude)
    )

# p300 mean amplitudes by group and condition (collapsed across region and hemisphere)
p300_data_grouped2 <- group_by(p300chans_data, Group, Condition)
summarise(p300_data_grouped2, # summarize operation by group
  mean = mean(Mean.Amplitude),
  std = sd(Mean.Amplitude)
    )
```

### Visualizations
```{r}
# p300 mean amplitude by group and condition (collapsed across region and hemisphere)
p300prime_data %>%
  mutate(Condition = fct_relevel(Condition,"Animal_primes", "Non-animal_primes","Animal_targets","Non-animal_targets/no_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Prime Type")

# p300 mean amplitude by group and condition (collapsed across region and hemisphere)
p300target_data %>%
  mutate(Condition = fct_relevel(Condition,"Animal_primes", "Non-animal_primes","Animal_targets","Non-animal_targets/no_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Target Type")

```

### Analyses
```{r}
p300prime_data$Group <- relevel(p300prime_data$Group, ref = "Aphasic")
#p300prime_data$Group <- relevel(p300prime_data$Group, ref = "Old Control")

# Run the model
p300_prime_model <- lmer(Mean.Amplitude ~ Condition*Group + (1|Participant.ID) + (1|Electrode), data=p300prime_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) 
tab_model(p300_prime_model, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df=TRUE)


p300target_data$Group <- relevel(p300target_data$Group, ref = "Aphasic")
#p300target_data$Group <- relevel(p300target_data$Group, ref = "Old Control")

# Run the model
p300_target_model <- lmer(Mean.Amplitude ~ Condition*Group + (1|Participant.ID) + (1|Electrode), data=p300target_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6)))
tab_model(p300_target_model, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df=TRUE)

```

## LPC Data
### Data Manipulations
```{r}
# Load data (2 data frames)
lpc_data <- read.csv(here("SYP Data","Submission 2 Data", "Mean Amplitudes", "lpc Mean Amps.csv"),stringsAsFactors=TRUE) # lpc mean amplitude data
#lpc_diffwave_data <- read.csv(here("SYP Data","Submission 2 Data", "Mean Amplitudes", "lpc Diff Waves Data.csv"),stringsAsFactors=TRUE) # lpc difference wave mean amplitude data

# Format data
lpc_data %<>%
  mutate(Group = factor(Group), 
         Condition = factor(Condition, levels=c("Non-animal_targets/no_primes","Delayed_masked_primes","Delayed_visible_primes","Immediate_masked_primes","Unrelated_primes")),
         Electrode = factor(Electrode),
         Mean.Amplitude = as.numeric(Mean.Amplitude))
str(lpc_data)

# lpc_diffwave_data %<>%
#   mutate(Group = factor(Group), 
#          Condition = factor(Condition, levels=c("np_minus_dmp","np_minus_dvp","np_minus_imp","up_minus_imp")),
#          Electrode = factor(Electrode),
#          Mean.Amplitude = as.numeric(Mean.Amplitude))
# str(lpc_diffwave_data)

# Create some data subsets
lpcchans_data <- subset (lpc_data,!grepl('T7|T8|AF3|AF4|Fp1|Fp2|Fpz|F3|Fz|F4|FC3|FCz|FC4',Electrode))

# Notes:
# Condition (for lpc data) = target condition; reference level (set above) = non-animal targets/no primes
# Condition (for lpc difference wave data) = difference wave condition;  reference level (set above) = No Primes - Delayed Masked Primes
```

### Descriptives
```{r}
# lpc mean amplitudes by groupe, condition, region, and hemisphere
lpc_data_grouped1 <- group_by(lpcchans_data, Group, Condition, Region, Hemisphere)
summarise(lpc_data_grouped1, # summarize operation by group
  mean = mean(Mean.Amplitude),
  std = sd(Mean.Amplitude)
    )

# lpc mean amplitudes by group and condition (collapsed across region and hemisphere)
lpc_data_grouped2 <- group_by(lpcchans_data, Group, Condition)
summarise(lpc_data_grouped2, # summarize operation by group
  mean = mean(Mean.Amplitude),
  std = sd(Mean.Amplitude)
    )
```

### Visualizations
```{r}
# lpc mean amplitude by group and condition (collapsed across region and hemisphere)
lpcchans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("")

# lpc mean amplitude by group and condition and region (collapsed across hemisphere)
lpcchans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Condition") +
  facet_wrap(~ factor(Region, c("Frontopolar","Frontal","Central","Parietal","Occipital")), nrow = 1)

# lpc mean amplitude by group and condition and hemisphere (collapsed across region)
lpcchans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Condition") +
  facet_wrap(~ Hemisphere, nrow = 1)

# lpc mean amplitude by group, condition, region, and hemisphere
lpcchans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(x=Condition, y=Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition") +
  facet_wrap(~Hemisphere + factor(Region, c("Frontopolar","Frontal","Central","Parietal","Occipital")))

# lpc mean amplitude by group and condition
lpcchans_data %>%
  mutate(Condition = fct_relevel(Condition,"Delayed_visible_primes","Delayed_masked_primes","Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Delayed masked primes
delayed_masked_data <- subset(lpcchans_data, Condition == "Delayed_masked_primes" | Condition == "Unrelated_primes" | Condition == "Non-animal_targets/no_primes")
delayed_masked_data %>%
  mutate(Condition = fct_relevel(Condition,"Non-animal_targets/no_primes","Delayed_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Delayed visible primes
delayed_visible_data <- subset(lpcchans_data,  Condition == "Delayed_visible_primes" | Condition == "Unrelated_primes" | Condition == "Non-animal_targets/no_primes")
delayed_visible_data %>%
  mutate(Condition = fct_relevel(Condition,"Non-animal_targets/no_primes","Delayed_visible_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Delayed primes
delayed_data <- subset(lpcchans_data, Condition == "Delayed_masked_primes" | Condition == "Delayed_visible_primes")
delayed_data %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Immediate masked primes
immediate_data<- subset(lpcchans_data, Condition == "Immediate_masked_primes" | Condition == "Unrelated_primes" | Condition == "Non-animal_targets/no_primes")
immediate_data %>%
  mutate(Condition = fct_relevel(Condition,"Non-animal_targets/no_primes","Immediate_masked_primes","Unrelated_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# Masked primes
masked_data<- subset(lpcchans_data, Condition == "Immediate_masked_primes" | Condition == "Delayed_masked_primes")
masked_data %>%
  mutate(Condition = fct_relevel(Condition,"Immediate_masked_primes","Delayed_masked_primes")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Mean Amplitude") +
  xlab("Priming Condition")

# lpc priming difference by group and condition (collapsed across region and hemisphere) - more negative = greater priming effect
lpc_diffwave_data %>%
  mutate(Condition = fct_relevel(Condition,"np_minus_dvp","np_minus_dmp","up_minus_imp","np_minus_imp")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Priming Difference") +
  xlab("Priming Condition") 

# Delayed primes comparison
delayed_diffwaves_data<- subset(lpc_diffwave_data, Condition == "np_minus_dvp" | Condition == "np_minus_dmp")
delayed_diffwaves_data %>%
  mutate(Condition = fct_relevel(Condition,"np_minus_dvp","np_minus_dmp")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Priming Difference") +
  xlab("Priming Condition") 

# Masked primes comparison
masked_diffwaves_data<- subset(lpc_diffwave_data, Condition == "up_minus_imp" | Condition == "np_minus_dmp"| Condition == "np_minus_imp")
masked_diffwaves_data %>%
  mutate(Condition = fct_relevel(Condition,"up_minus_imp","np_minus_dmp", "np_minus_imp")) %>%
  ggplot(aes(Condition, Mean.Amplitude, group=Group, color=Group)) +
  stat_summary(geom="pointrange", fun.data = mean_cl_boot) +
  stat_summary(geom="line",fun.data = mean_cl_boot)+
  ylab("Priming Difference") +
  xlab("Priming Condition") 

```

### Analyses
```{r}
lpcchans_data$Condition <- factor(lpcchans_data$Condition, levels=c("Non-animal_targets/no_primes","Delayed_visible_primes","Delayed_masked_primes","Immediate_masked_primes","Unrelated_primes"))
contrasts(lpcchans_data$Condition)<-contr.treatment(levels(lpcchans_data$Condition))/5

# lpcchans_data$Condition <- factor(lpcchans_data$Condition, levels=c("Delayed_visible_primes","Delayed_masked_primes","Immediate_masked_primes","Unrelated_primes","Non-animal_targets/no_primes"))
# contrasts(lpcchans_data$Condition)<-contr.sdif(levels(lpcchans_data$Condition))/5

lpcchans_data$Group <- relevel(lpcchans_data$Group, ref = "Old Control")
#lpcchans_data$Group <- relevel(lpcchans_data$Group, ref = "Aphasic")
contrasts(lpcchans_data$Group)<-contr.treatment(levels(lpcchans_data$Group))/2

# Run the model
lpc_omnibus <- lmer(Mean.Amplitude ~ Condition*Group + (1|Participant.ID) + (1|Electrode), data=lpcchans_data, REML=FALSE,control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=1e6))) 
tab_model(lpc_omnibus, show.se = TRUE,show.ci = FALSE, show.stat = TRUE, show.df=TRUE)

```



